---
title: "Plottings on Instacart Dataset"
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```

Create a flexdashboard using plotly for that includes at least three distinct plot types (e.g. scatterplots, line plots, bar plots, box plots, etc.). Use one of the following datasets, and load from the p8105.datasets package:


The following plots are based on the dataset instacart under the filter of selecting orders placed on Friday, Saturday and Sunday to investigate the shopping customs of weekend orders. 

## 1. Barplot

This is a barplot of the orders on instacart on weekends, organized by the departments. We could see the highest three departments shopped from are produce, dairy eggs and beverages.  
```{r}
data(instacart)

instacart_weekends= filter(instacart, order_dow== 5:7, preserve= TRUE)

instacart_weekends %>%
  count(department) %>%
  mutate(department = fct_reorder(department, n)) %>% 
  plot_ly(x = ~department, y = ~n, color = ~ department, type = "bar", colors = "viridis")

```

## 2. Boxplot

This is a boxplot on when the orders are placed in a day on weekends by departments. 
```{r}
instacart_weekends %>% 
  mutate(department = fct_reorder(department, order_hour_of_day)) %>% 
  plot_ly(y= ~ order_hour_of_day, color= ~department, type= "box", colors="viridis")
```
## 3. Scatterplot

This is a scatterplot on the the orders of instacarts on weekends. 
This is a box plot on when the orders are placed in a day on weekends by departments.
The scatter plot the location and the time (id of aisle and the time of order placed) by department. The degree of transparency of the points denotes the frequency of the orders in the given hour, aisle and department. 
```{r}

instacart_weekends %>%
  mutate(text_label = str_c("Departments", department, "Hour ", order_hour_of_day)) %>%
  plot_ly(
    x = ~aisle_id, y = ~order_hour_of_day, type = "scatter", mode = "markers",
    color = ~department, alpha = 0.1, colors="viridis")

```

